Autoregressive example

### 2020-10-17 src/s_ar1.Rmd
added older versions of the ar1 experiments

nreplicates <- 100
r_star_vals <- vector(length = nreplicates)
r_hat_vals <- vector(length = nreplicates)
for(i in 1:nreplicates){
    print(i)

@@

caretGrid <- tibble(mtry=2)

rand_samples <- sample(1:nrow(full_data), 0.7 * nrow(full_data))
training_data <- full_data[rand_samples, ]
testing_data <- full_data[-rand_samples, ]
gbmFit1 <- train(chain ~ ., data = training_data, 
                 method = "rf",
                 trControl = trainControl(method = 'none'), 
                    tuneGrid = caretGrid, verbose=FALSE)

>>>>

nreplicates <- 1000
r_star_vals <- vector(length = nreplicates)
r_hat_vals <- vector(length = nreplicates)
for(i in 1:nreplicates){
  if(i%%100==0)
    print(i)

@@

caretGrid <- expand.grid(interaction.depth=c(3), n.trees = 50,
                   shrinkage=c(0.1),
                   n.minobsinnode=10)

rand_samples <- sample(1:nrow(full_data), 0.7 * nrow(full_data))
training_data <- full_data[rand_samples, ]
testing_data <- full_data[-rand_samples, ]
gbmFit1 <- train(chain ~ ., data = training_data, 
                 method = "gbm",
                 trControl = trainControl(method = 'none'), 
                    tuneGrid = caretGrid, verbose=FALSE)
